\section{Recent developments}
\begin{frame}{Current use and recent developments}
  \begin{itemize}
  \item It look as if the development of \Okis{Customizer} has been
    taken up again. Must have a look into it.
  \item In Venlo we do not use the repository anymore during the
    exam.
    \begin{itemize}
    \item The students are relieved of  sometimes error prone checking
      out and committing.
    \item Less technical problems with modern laptops and Ethernet drivers.
    \item Some laptops (Think Bitten Fruit Shop in Cupertino, CA) do not have an
      Ethernet connector anymore.
    \item Less possibility of cheating\InlineCinical.
    \item Although handling all sticks two times per exam, the overall
      logistics is simpler and quicker
    \end{itemize}
  \end{itemize}
\end{frame}
\subsection{Current features}
\begin{frame}[shrink]{Features and apps}
\begin{itemize}
\item Boot to desktop, no password, for USB 2 and USB 3\footnote{Some
    older laptops will not boot from their USB 3 port} ports.
\item No access to local media except stick
\item No access to wired or wireless network, nor bluetooth
\end{itemize}
Installed apps:{\scriptsize
\begin{multicols}{2}
  \begin{itemize}
  \item Java 8
  \item Netbean IDE 8.2
  \item FX Scene Builder 2.0
  \item Glassfish 4.1.1.
  \item Apache httpd server 2.4.7
  \item Apache Tomcat server 8.0.27
  \item Postgresql 9.6.0
  \item PgAdmin-III
  \item Libreoffice 5
  \item git (cli)
  \item subversion (cli)
  \item rapidsvn 
  \item Pyhton 2.7 and 3
  \item PHP5+7 (server and CLI)
  \item R + R-studio
  \item nodejs
  \item Complete Latex Installation
  \end{itemize}
\end{multicols}}
\begin{itemize}
\item All with a total installed weight of 3.5 GB. (Including student
  work space 4.5 GB = image size). The first Partition currently is
  6GB big.
\item As you can see we are prepared for almost any programming or
  other IT related exam.
\end{itemize}
\end{frame}

